---
title: "Weight of Fish"
author: "Larissa Vera"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch

Find the best 2 predictors for the weight of the perch.

```{r}
Perchwtall=lm(Weight~.-Weight,data=Perch)
summary.lm(Perchwtall)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
##Which is best??  

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```

```{r}
best.model <- lm(Weight~Height+Width,data=Perch)
summary(best.model)
```

```{r}
anova(best.model,Perchwtall)
```


### Best Models
the best model is all the variables 

### Best Two regressor model
the model using height and width

## Pike

```{r}
Pikewtall=lm(Weight~.-Weight,data=Pike)
summary.lm(Pikewtall)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```

```{r}
best.model <- lm(Weight~Height+Width,data=Pike)
summary(best.model)
```

```{r}
anova(best.model,Pikewtall)
```

### Best Models

the best model is all the variables 

### Best Two regressor model

the model using height and width 

## Roach

```{r}
Roachwtall=lm(Weight~.-Weight,data=Roach)
summary.lm(Roachwtall)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```

```{r}
best.model <- lm(Weight~Height+Width,data=Roach)
summary(best.model)
```

```{r}
anova(best.model,Roachwtall)
```

### Best Models

the best model is all the variables 

### Best Two regressor model

the model height and width

## Final Summary Statements

In conclusion the helper file used is bestsubset regression. the best regresser model for perch were height and width. The best regressor model for pike was length1 and length 3. the best regression model for roach were length3 and width in perch, pike, and roach all the variables were the best model


